Response to Reviewers $Rev^1$

### 2020-03-17 ICT_Frontiers_rev202001_reply.tex
update

    	\begin{ans}
    		\begin{enumerate}
    			\item In this article, the definition of coarse-graining is our "Definition 1" (line: \lineref{line:r2q1-1}). Coarse-graining is simply a function which maps a stochastic process $X$ with state space $\mathcal{X}$ to a stochastic process $Y$ with state space $\mathcal{Y}$. As we explained in Footnote 2, functions in the mathematical sense used here are always either one-to-one or many-to-one. We do not constrain ICT to be applied to any specific classes of coarse-graining.
    			Thank the reviewer for proposing the question about the relationship between NTIC and scale of coarse-graining. We currently know that NTIC is not a non-monotonic function of the scale of coarse-graining. Some coarse-grainings lead to higher NTICs for macroscopic than microscopic processes. However, we are just starting the research on this relationship, and have not yet had a systematic understanding of it. This work may involve the technique of partial information decomposition and related research fields. 
    			We agree that our original claim about existing a intermediate maxima in NTIC was too strong.

    			We hope to address this question in future research.

    			We emphasise the non-monotonic relation between the scales of coarse-graining and the degrees of NTIC. However, we do not exclude the possibility that there exist multiple NTIC picks across scales of coarse-graining of a process. 
    			This implies that we do not exclude the possibility that there exist multiple high conscious processes at different scales. 
    			(However, due to IC, conscious processes are not able to know the existence of each other. 
    			\revise{\lineref{line:non-monotonic}}
    			{
    				It is important to note that NTIC can be a non-monotonic function of the scale of coarse-graining. We saw above that not sufficiently coarse-grained variables have low values of NTIC. On the other hand, overly coarse-grained macroscopic variables  also result in low values of NTIC. For example, in an extreme scenario, when all microscopic states map to a single macroscopic variable, the macroscopic level does not have any information capacity and thus cannot have high mutual information across time steps. Therefore, only processes at a certain level of coarse-graining in the neural system can form a high degree of NTIC (Fig.~\ref{fig:LevelOfConsciousness}). ICT indicates that human consciousness occurs at the level of coarse-graining where higher NTIC is formed within the neural system.
    			}
    			{
    				It is important to note that NTIC can be a non-monotonic function of the scale of coarse-graining. Insufficiently coarse-grained variables could lead to lower values of NTICs at micro than macroscopic processes. On the other hand, overly coarse-grained macroscopic variables also result in low values of NTIC. For example, in an extreme scenario, when all microscopic states map to a single macroscopic variable, the macroscopic level does not have any information capacity and thus cannot have high mutual information across time steps. Therefore, processes at certain levels of coarse-graining may have higher values of NTIC than other levels (Fig.~\ref{fig:LevelOfConsciousness}). ICT suggests that human consciousness occurs at the level of coarse-graining where higher NTIC is formed within the neural system.
    			}										
    			\item \toWrite{TBD}
%    			\item \toWrite{After replying the first reviewer}
    		\end{enumerate}

@@

    	\begin{ans}
			We followed a common setting of coarse-graining (e.g. \cite{PFANTE.2014}) which does not and should not take time $Y_t=f_Y(X_t)$ (in Definition 1). Coarse-graining is merely a function which maps microstates of a system to macrostates, and the microstates and the macrostates are simply different level of descriptions of a system. 
			Following this setting, the definition of information closure (flow) $J_{t}(X \rightarrow Y )$ can also be applied in the sense of coarse-graining.

>>>>

    	\begin{ans}
    		Thank the reviewer for the critical comments. We have replied these comments in details in the following Q\&A. 
%    		\begin{enumerate}
%    			\item In this article, the definition of coarse-graining is our "Definition 1" (line: \lineref{line:r2q1-1}). Coarse-graining is simply a function which maps a stochastic process $X$ with state space $\mathcal{X}$ to a stochastic process $Y$ with state space $\mathcal{Y}$. As we explained in Footnote 2, functions in the mathematical sense used here are always either one-to-one or many-to-one. We do not constrain ICT to be applied to any specific classes of coarse-graining.
%    			Thank the reviewer for proposing the question about the relationship between NTIC and scale of coarse-graining. We currently know that NTIC is not a non-monotonic function of the scale of coarse-graining. Some coarse-grainings lead to higher NTICs for macroscopic than microscopic processes. However, we are just starting the research on this relationship, and have not yet had a systematic understanding of it. This work may involve the technique of partial information decomposition and related research fields. 
%    			We agree that our original claim about existing a intermediate maxima in NTIC was too strong. 
%    			
%    			
%    			We hope to address this question in future research. 
%    			
%    			
%    			
%    			We emphasise the non-monotonic relation between the scales of coarse-graining and the degrees of NTIC. However, we do not exclude the possibility that there exist multiple NTIC picks across scales of coarse-graining of a process. 
%    			This implies that we do not exclude the possibility that there exist multiple high conscious processes at different scales. 
%    			(However, due to IC, conscious processes are not able to know the existence of each other. 
%    			\revise{\lineref{line:non-monotonic}}
%    			{
%    				It is important to note that NTIC can be a non-monotonic function of the scale of coarse-graining. We saw above that not sufficiently coarse-grained variables have low values of NTIC. On the other hand, overly coarse-grained macroscopic variables  also result in low values of NTIC. For example, in an extreme scenario, when all microscopic states map to a single macroscopic variable, the macroscopic level does not have any information capacity and thus cannot have high mutual information across time steps. Therefore, only processes at a certain level of coarse-graining in the neural system can form a high degree of NTIC (Fig.~\ref{fig:LevelOfConsciousness}). ICT indicates that human consciousness occurs at the level of coarse-graining where higher NTIC is formed within the neural system.
%    			}
%    			{
%    				It is important to note that NTIC can be a non-monotonic function of the scale of coarse-graining. Insufficiently coarse-grained variables could lead to lower values of NTICs at micro than macroscopic processes. On the other hand, overly coarse-grained macroscopic variables also result in low values of NTIC. For example, in an extreme scenario, when all microscopic states map to a single macroscopic variable, the macroscopic level does not have any information capacity and thus cannot have high mutual information across time steps. Therefore, processes at certain levels of coarse-graining may have higher values of NTIC than other levels (Fig.~\ref{fig:LevelOfConsciousness}). ICT suggests that human consciousness occurs at the level of coarse-graining where higher NTIC is formed within the neural system.
%    			}										
%    			\item 
%    			\item
%    		\end{enumerate}

@@

    	\begin{ans}
			We followed the common setting of coarse-graining (e.g. \cite{PFANTE.2014}) which does not and should not take time $Y_t=f_Y(X_t)$ (in Definition 1). Coarse-graining is merely a function which maps microstates of a system to macrostates, and the microstates and the macrostates are simply different level of descriptions of a system. 
			Following this setting, the definition of information closure (flow) $J_{t}(X \rightarrow Y )$ can also be applied in the sense of coarse-graining.
